Measuring E-Mail Header Injections on the World Wide Web

### 2016-10-25 Background/history.tex
LaTeX tricks to get us down to 9.25

\subsection{History of \ehi}

We found the first \ehi description in a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how an \ehi vulnerability existed in the implementation of the \texttt{mail()} function in PHP and how it can be exploited. More recently, a blog post by Damon Kohler~\cite{DK} and an accompanying wiki article~\cite{Injection} describe the attack vector and outline few defense measures for \ehi vulnerabilities.

@@

\input{Background/php.tex}

% TODO: Change all domains to example.com - DONE.
% TODO: Sai, this is the first time we mention SMTP, need more background and a reference to the RFC.

\begin{sloppypar}
When this code is given the malicious input \texttt{\lstinline{abc@example.com\\nCC:spc@example.com}} as the value of the \texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}, it generates the equivalent SMTP Headers shown in Listing~\ref{code:smtpheaders}. It can be seen that the \texttt{CC} (carbon copy) header that we injected appears as part of the resulting SMTP message. This will make the e-mail get sent to the e-mail address specified as part of the \texttt{CC} as well. 
\input{Background/smtpheaders}
%\input{Background/history_table}
\end{sloppypar}

>>>>

\subsection{History of \ehi}
\input{Background/php.tex}
We found the first \ehi description in a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo| describing how an \ehi vulnerability existed in the implementation of the \texttt{mail()} function in PHP and how it can be exploited. More recently, a blog post by Damon Kohler~\cite{DK} and an accompanying wiki article~\cite{Injection} describe the attack vector and outline few defense measures for \ehi vulnerabilities.

@@

\input{Background/smtpheaders}
\begin{sloppypar}
When this code is given the malicious input \texttt{\lstinline{abc@example.com\\nCC:spc@example.com}} as the value of the \texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}, it generates the equivalent SMTP Headers shown in Listing~\ref{code:smtpheaders}. It can be seen that the \texttt{CC} (carbon copy) header that we injected appears as part of the resulting SMTP message. This will make the e-mail get sent to the e-mail address specified as part of the \texttt{CC} as well.

%\input{Background/history_table}
\end{sloppypar}

%TODO Adam: added this para abt E-Mail Header Injection history from CVE
We gathered reported Common Vulnerabilities and Exposures
(CVE)~\cite{cve} to get an idea of the distribution of
reported \ehi over time. We found 28 reports of \ehi, shown in
Table~\ref*{tab:history}. From the table, it can be seen that even though many \ehi vulnerabilities were found in the earlier years (2005-07), there have been several recently discovered \ehi vulnerabilities which suggests that it is still a very real threat and is relevant to modern web security.

\input{Background/history_table}

### 2016-10-25 Background/impact.tex
LaTeX tricks to get us down to 9.25

The impact of an \ehi vulnerability can be far-reaching. According to
w3tech, PHP, Java, Python, and Ruby (combined) account for over
85\%\,\footnotemark{} of the server-side programming languages in
websites measured, and the default implementation of the \email functionality of these languages is vulnerable to \ehi.

\footnotetext{A website may use more than one server-side programming language.}

>>>>

The impact of an \ehi vulnerability can be far-reaching. According to
w3tech, PHP, Java, Python, and Ruby (combined) account for over
85\%\, of the server-side programming languages in
websites measured, and the default implementation of the \email functionality of these languages is vulnerable to \ehi.

### 2016-10-25 Background/pbm_bg.tex
LaTeX tricks to get us down to 9.25

\ehi belongs to a broad class of vulnerabilities known as command injection vulnerabilities. However, unlike its more popular siblings, SQL injection~\cite{sql1, sql0, sql2}, Cross-Site Scripting~\cite{Injection1, KleinAmit}, or HTTP Header Injection~\cite{sessionride}, relatively little research is available on \ehi vulnerabilities.

As with other vulnerabilities in this class, \ehi is caused due to improper or nonexistent sanitization of user input. If the program that constructs \emails from user input fails to check for the presence of \email headers in the user input, a malicious user---using a well-crafted payload---can control the headers set for this particular e-mail. \ehi vulnerabilities can be leveraged to enable malicious attacks, including, but not limited to, spoofing or phishing.

>>>>

\ehi belongs to the class of command injection vulnerabilities. However, unlike its more popular siblings, SQL injection~\cite{sql1, sql0, sql2}, Cross-Site Scripting~\cite{Injection1, KleinAmit}, or HTTP Header Injection~\cite{sessionride}, relatively little research is available on \ehi vulnerabilities.

As with other command injection vulnerabilities, \ehi is caused by
improper or nonexistent sanitization of user input. If the program
constructs \emails from user input and fails to check for the presence
of \email headers, a malicious user can control the headers of this particular e-mail. \ehi vulnerabilities can be leveraged to enable malicious attacks, including, but not limited to, spoofing or phishing.

### 2016-10-25 Discussion/limits.tex
9.75
LaTeX tricks to get us down to 9.25

		\begin{table}
			\centering
			\scriptsize
			\begin{tabular}{|p{4cm}|c|c|}
				\hline
				\multicolumn{1}{|c}{\textbf{Method}} &
				\multicolumn{1}{|c|}{\textbf{Running time}} &
				\multicolumn{1}{|c|}{\textbf{Slowdown}}
				\\
				\hline
				\centering Using our pipeline & 629.043 & - \\
				\hline
				\centering Our pipeline with Selenium & 919.372 & \slowSelenium \\
				\hline				
				\centering Parsing \email fields instead of `grep'ing inside form & 707.154 & \slowParse \\								
				\hline
			\end{tabular}
			\caption[\titlecap{}]{Running times in seconds for crawling, parsing, and detecting presence of \email fields in 1000 random wikipedia pages.}
			\label{tab:perf}
		\end{table}

@@

        The parser that we use for HTML parsing---Beautiful Soup---does not parse malformed HTML and throws an exception on encountering malformed HTML. Thus, we have designed the system to exit gracefully on such occasions. A side-effect of this is that our system is unable to test web applications with bad HTML markup\,\footnotemark.

        \footnotetext{We do not have any data about whether bad markup indicates an overall lower quality of the web application, and thus cannot comment on whether such websites are more likely to have vulnerabilities.}

>>>>

		\begin{table}
			\centering
			\scriptsize
			\begin{tabular}{|p{4cm}|c|c|}
				\hline
				\multicolumn{1}{|c}{\textbf{Method}} &
				\multicolumn{1}{|c|}{\textbf{Running time}} &
				\multicolumn{1}{|c|}{\textbf{Slowdown}}
				\\
				\hline
				\centering Using our pipeline & 629.043 & - \\
				\hline
				\centering Our pipeline with Selenium & 919.372 & \slowSelenium \\
				\hline				
				\centering Parsing \email fields instead of `grep'ing& 707.154 & \slowParse \\								
				\hline
			\end{tabular}
			\caption[\titlecap{}]{Running times in seconds for crawling, parsing, and detecting presence of \email fields in 1000 random wikipedia pages.}
            \vspace{-5ex}
			\label{tab:perf}
		\end{table}

@@

        The parser that we use for HTML parsing---Beautiful Soup---does not parse malformed HTML and throws an exception on encountering malformed HTML. Thus, we have designed the system to exit gracefully on such occasions. A side-effect of this is that our system is unable to test web applications with bad HTML markup.

### 2016-10-25 System/components.tex
LaTeX tricks to get us down to 9.25

The \Email Field Checker searches for the words \texttt{e-mail}, \texttt{mail} or \texttt{email} within the form, instead of an explicit HTML5 \email field (e.g.,\ {\lstinline{<input type="email">}}). This is by design, taking into account a common design pattern used by web developers, where they may have a text field with an \texttt{id} or \texttt{name} attribute set to \texttt{email}, instead of an actual \email type attribute, for purposes of backward compatibility with older browsers.

@@

The output of this stage is stored in the database for persistence and acts as the input to the Payload Injection module.

@@

We created four different malicious payloads. Each of these payloads is crafted for a particular use case. The four payloads are:

\begin{enumerate}
	\item
	\texttt{nuser(xxxx)@example.com\textbackslash{}n\\bcc:maluser(xxxx)@example.com}

	\item \texttt{nuser(xxxx)@example.com\textbackslash{}n\\bcc:maluser(xxxx)@example.com\textbackslash{}nx-check:in}

	\item \texttt{nuser(xxxx)@example.com\textbackslash{}r\textbackslash{}n\\bcc:maluser(xxxx)@example.com}

	\item \texttt{nuser(xxxx)@example.com\textbackslash{}r\textbackslash{}n\\bcc:maluser(xxxx)@example.com\textbackslash{}r\textbackslash{}nx-check:in}

\end{enumerate}
Payload 1 is the most minimal payload: it injects a newline character followed by the \texttt{bcc} field. Payload 2 contains the additional \texttt{x-check} header to inject Python-based web applications. Payloads 3 and 4 are added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems.~\cite{rfc2616}

@@

\label{analyze:detect_x_check}
\noindent\textbf{Detecting injected \texttt{x-check} headers}
\Emails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of \emails.
These \emails could have been generated due to two reasons:
\begin{enumerate}
	\item The web application performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending \emails only to the \texttt{nuser} account. These \emails then act as proof that the vulnerability was not found on the given URL.
	\item The \texttt{bcc} header can be ignored for other reasons (e.g.,\ Python's default behavior when it encounters duplicate headers). In this case, we check if the \email contains the custom header \texttt{x-check}. If it does, then this is a successful exploit of the vulnerability.
\end{enumerate}

>>>>

The \Email Field Checker searches for the words \texttt{e-mail},
\texttt{mail} or \texttt{email} within the form, instead of an
explicit HTML5 \email field (e.g.,\ {\lstinline{<input type="email">}}). This is by design, taking into account a common
design pattern used by web developers, where they may have a text
field with an \texttt{id} or \texttt{name} attribute set to
\texttt{email}, instead of an actual \email type attribute, for
purposes of backward compatibility with older browsers. The output of this stage is stored in the database for persistence and acts as the input to the Payload Injection module.

@@

@@

We created four different malicious payloads. Each of these payloads
is crafted for a particular use case. The four payloads are:
(1) nuser(xxxx)@example.com\textbackslash{}n\-bcc:\-maluser\-(xxxx)\-@example.com,
(2) nuser(xxxx)@\-example.com\textbackslash{}n\-bcc:\-maluser\-(xxxx)\-@example.com\textbackslash{}n\-x-check:in,
(3) nuser(xxxx)@\-example.com\textbackslash{}r\textbackslash{}n\-bcc:\-maluser(xxxx)\-@example.com,
and (4) nuser(xxxx)\-@example.com\textbackslash{}r\textbackslash{}n\-bcc:\-maluser(xxxx)\-@example.\-com\textbackslash{}r\textbackslash{}n\-x-check:in.

Payload 1 is the most minimal payload: it injects a newline character followed by the \texttt{bcc} field. Payload 2 contains the additional \texttt{x-check} header to inject Python-based web applications. Payloads 3 and 4 are added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems.~\cite{rfc2616}

@@

\label{analyze:detect_x_check}
\noindent\textbf{Detecting injected \texttt{x-check} headers} \Emails
not received by the \texttt{maluser} account but by the \texttt{nuser}
account constitute a special category of \emails. These \emails could
have been generated due to two reasons: (1) The web application
performed some sanitization routines and stripped out the \texttt{bcc}
part of the payload, thereby sending \emails only to the
\texttt{nuser} account. These \emails then act as proof that the
vulnerability was not found on the given URL. (2) The \texttt{bcc}
header can be ignored for other reasons (e.g.,\ Python's default
behavior when it encounters duplicate headers). In this case, we check
if the \email contains the custom header \texttt{x-check}. If it does,
then this is a successful exploit of the vulnerability.

### 2016-10-25 abstract.tex
updated the abstract with info on malicious content
LaTeX tricks to get us down to 9.25

\begin{abstract}
	\ehi vulnerability is a class of vulnerability that can occur in web applications that use user input to construct \email messages. \ehi is possible when the mailing script fails to check for the presence of \email headers in user input (either form fields or URL parameters). We discovered that the vulnerability exists in the reference implementation of the built-in \email functionality in the popular languages PHP, Java, Python, and Ruby. With the proper injection string, this vulnerability can be exploited to allow an attacker to inject additional headers, modify existing headers, and alter the content of the \email.

	While \ehi vulnerabilities are known by the community, and some commercial vulnerability scanners claim to discover \ehi vulnerabilities, they have never been studied by the academic community. This paper presents a scalable mechanism to automatically detect \ehi vulnerabilities and uses this mechanism to quantify the prevalence of \ehi vulnerabilities on the web. Using a black-box testing approach, the system crawled \urls URLs to identify web pages which contained form fields. \forms such forms were found by the system, of which \emailforms forms contained \email fields. We then fuzzed \fuzzed forms to see if they would send us an \email, and \recd forms sent us an \email. Of these, \malfuzzed forms were tested with \ehi payloads and, of these, we found \success vulnerable URLs across \domains domains. Then, to measure if \ehi vulnerabilities are actively being exploited to create a spamming platform, we found evidence that \ipsblacklist IPs that were vulnerable to \ehi are on spamming blacklists. This work shows that \ehi vulnerabilities are widespread and deserve future research attention.
\end{abstract}

>>>>

\begin{abstract}
	\ehi vulnerability is a class of vulnerability that can occur in web applications that use user input to construct \email messages. \ehi is possible when the script fails to check for the presence of \email headers in user input. We discovered that the vulnerability exists in the built-in \email functionality of the popular languages PHP, Java, Python, and Ruby. With the proper injection string, this vulnerability can be exploited to allow an attacker to inject additional headers, modify existing headers, and alter the content of the \email.

	While \ehi vulnerabilities are known by the community, and some commercial vulnerability scanners claim to discover \ehi vulnerabilities, they have never been studied by the academic community. This paper presents a scalable mechanism to automatically detect \ehi vulnerabilities and uses this mechanism to quantify the prevalence of \ehi vulnerabilities on the web. Using a black-box testing approach, the system crawled \urls URLs to identify web pages which contained form fields. \forms such forms were found by the system, of which \emailforms forms contained \email fields. We then fuzzed \fuzzed forms to see if they would send us an \email, and \recd forms sent us an \email. Of these, \malfuzzed forms were tested with \ehi payloads and, of these, we found \success vulnerable URLs across \domains domains. Then, to measure if \ehi vulnerabilities are actively being exploited to create a spamming platform, we found evidence that \ipsblacklist IPs that were vulnerable to \ehi are on spamming blacklists. We also performed a virus check on the received \emails and found 265 domains to be sending malicious content. This work shows that \ehi vulnerabilities are widespread and deserve future research attention.
\end{abstract}

### 2016-10-25 introduction.tex
LaTeX tricks to get us down to 9.25

\section{Introduction}
The World Wide Web has single-handedly brought about a change in the way we use computers. The ubiquitous nature of the web has made it possible for anyone to access information and services anywhere and on multiple devices such as phones, laptops, TVs, and cars. This access has ushered in an era of web applications which depend on user input. 
While the rapid pace of development has improved the speed of information dissemination, it comes at a cost. As users move more and more of their personal and financial information to web applications, attackers are responding by using web application vulnerabilities to access this lucrative data.

@@

To shed light on this little-studied vulnerability class, we describe \ehi vulnerabilities and measure \ehi vulnerabilities on the web. To perform this measurement, we crawled the web, extracted forms with \email fields, and injected them with different payloads to infer the existence of an \ehi vulnerability. We then audited received \emails to see if any of the injected data was present. This allowed us to classify whether a particular URL was vulnerable to the attack. Our automated system works in a black-box manner, without looking at the web application's source code, and only analyzes the \emails we receive based on the injected payloads.
%TODO Adam: Added a line to make clear that we wanted a quantification before attempting something like a source-code analyzer. This addresses reviewer 690B's concerns.

The objective of our research is to study the prevalence of this vulnerability on the World Wide Web and identify whether further research is required in this area.
In summary, we make the following contributions:
\begin{itemize}

\item We develop a black-box approach to detect \ehi vulnerabilities in a web application.

\item We develop an open-source system to crawl the web and automatically detect \ehi vulnerabilities.

\item We use our system to crawl \urls URLs, and we find \success URLs vulnerable to \ehi across \domains domains.

\end{itemize}

>>>>

\section{Introduction}
The World Wide Web has single-handedly brought about a change in the way we use computers. The ubiquitous nature of the web made it possible for anyone to access information and services anywhere and on multiple devices such as phones, laptops, TVs, and cars. This access has ushered in an era of web applications which depend on user input. 
While the rapid pace of development has improved the speed of
information dissemination, it comes at a cost. As users move more and
more of their personal and financial information to web applications,
attackers are responding by using web application vulnerabilities to steal lucrative data.

@@

To shed light on this little-studied vulnerability class, we describe
\ehi vulnerabilities and measure \ehi vulnerabilities. To perform this
measurement, we crawled the web, extracted forms with \email fields,
and injected them with different payloads to infer the existence of an
\ehi vulnerability. We then audited received \emails to see if any of
the injected data was present. This allowed us to classify whether a
particular URL was vulnerable to the attack. Our automated system
works in a black-box manner, without looking at the web application's
source code, and only analyzes the paylods of the \emails.
%TODO Adam: Added a line to make clear that we wanted a quantification before attempting something like a source-code analyzer. This addresses reviewer 690B's concerns.

In summary, we make the following contributions:
\begin{itemize}

\item We develop a black-box approach to detect \ehi vulnerabilities in a web application.
\vspace{-2ex}
\item We develop an open-source system to crawl the web and automatically detect \ehi vulnerabilities.
\vspace{-2ex}
\item We use our system to crawl \urls URLs, and we find \success URLs vulnerable to \ehi across \domains domains. 
\vspace{-2ex}
\end{itemize}

### 2016-10-25 paper.tex
LaTeX tricks to get us down to 9.25

% default options for listings
\usepackage{listings}
\usepackage{listingsutf8}
\usepackage{textcomp}     % access \textquotesingle
\lstset{
	backgroundcolor=\color{lightgray},
	basicstyle=\scriptsize{}\ttfamily,
	breaklines=true, 
	captionpos=b,
	commentstyle=\color{darkgreen}, 
	frame=single,
	keywordstyle=\color{blue}, 
	numbers=left,
	numbersep=5pt,
	numberstyle=\tiny\color{mygray},
	rulecolor=\color{black},
	showstringspaces=false,
	upquote=true
}

@@

	\author{
		% You can go ahead and credit any number of authors here,
		% e.g. one 'row of three' or two rows (consisting of one row of three
		% and a second row of one, two or three).
		%
		% The command \alignauthor (no curly braces needed) should
		% precede each author name, affiliation/snail-mail address and
		% e-mail address. Additionally, tag each line of
		% affiliation/address with \affaddr, and tag the
		% e-mail address with \email.
		%
		% 1st. author
		\alignauthor
		Sai Prashanth Chandramouli$^\dag$, Pierre-Marie Bajan$^\S$, Christopher Kruegel$^\ddag$, Giovanni Vigna$^\ddag$, Ziming Zhao$^\dag$, Adam Doup\'e$^\dag$, and Gail-Joon Ahn$^\dag$\\
		\affaddr{Arizona State University$^\dag$, IRT SystemX and the Telecom SudParis$^\S$, and University of California, Santa Barbara$^\ddag$}\\
		\{saipc, zzhao30, doupe, gahn\}@asu.edu$^\dag$,
        pierre-marie.bajan@irt-systemx.fr$^\S$, \\
        \{chris, vigna\}@cs.ucsb.edu$^\ddag$
        }
		% 2nd. author
		%% \alignauthor

		%% \affaddr{University of California, Santa Barbara}\\
		%% pm.bajan@free.fr
		%% \alignauthor
		%% \\
		%% \affaddr{University of California, Santa Barbara}\\
		%% giovanni.vigna@gmail.com
		%% \and
		%% \alignauthor
		%% \\
		%% \affaddr{Arizona State University}\\
		%% Ziming.Zhao@asu.edu
		%% \alignauthor
		%% Adam Doup\'{e}\\
		%% \affaddr{Arizona State University}\\
		%% doupe@asu.edu
		%% \alignauthor
		%% Gail-Joon Ahn\\
		%% \affaddr{Arizona State University}\\
		%% Gail-Joon.Ahn@asu.edu
		% 3rd. author
		%% \alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
		%% 	one who did all the really hard work.}\\
		%% \affaddr{The Th{\o}rv{\"a}ld Group}\\
		%% \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
		%% \affaddr{Hekla, Iceland}\\
		%% \email{larst@affiliation.org}
		%% \and  % use '\and' if you need 'another row' of author names
		%% % 4th. author
		%% \alignauthor Lawrence P. Leipuner\\
		%% \affaddr{Brookhaven Laboratories}\\
		%% \affaddr{Brookhaven National Lab}\\
		%% \affaddr{P.O. Box 5000}\\
		%% \email{lleipuner@researchlabs.org}
		%% % 5th. author
		%% \alignauthor Sean Fogarty\\
		%% \affaddr{NASA Ames Research Center}\\
		%% \affaddr{Moffett Field}\\
		%% \affaddr{California 94035}\\
		%% \email{fogartys@amesres.org}
		%% % 6th. author
		%% \alignauthor Charles Palmer\\
		%% \affaddr{Palmer Research Laboratories}\\
		%% \affaddr{8600 Datapoint Drive}\\
		%% \affaddr{San Antonio, Texas 78229}\\
		%% \email{cpalmer@prl.com}
	% There's nothing stopping you putting the seventh, eighth, etc.
	% author on the opening page (as the 'third row') but we ask,
	% for aesthetic reasons that you place these 'additional authors'
	% in the \additional authors block, viz.
	%% \additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
	%% 	email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
	%% 	(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
	%% \date{30 July 1999}
	% Just remember to make sure that the TOTAL number of authors
	% is the number that will appear on the first page PLUS the
	% number that will appear in the \additionalauthors section.
	\renewcommand{\email}{e-\nobreak{}mail\xspace}
	\maketitle
	\input{abstract}

>>>>

% default options for listings
\usepackage{listings}
\usepackage{listingsutf8}
\usepackage{textcomp}     % access \textquotesingle
\lstset{
	backgroundcolor=\color{lightgray},
	basicstyle=\scriptsize{}\ttfamily,
	breaklines=true, 
	captionpos=b,
	commentstyle=\color{darkgreen}, 
	frame=single,
	keywordstyle=\color{blue}, 
	numbers=left,
	numbersep=5pt,
	numberstyle=\tiny\color{mygray},
	rulecolor=\color{black},
	showstringspaces=false,
	upquote=true,
    belowskip=-6ex,
}

@@

	\author{
		% You can go ahead and credit any number of authors here,
		% e.g. one 'row of three' or two rows (consisting of one row of three
		% and a second row of one, two or three).
		%
		% The command \alignauthor (no curly braces needed) should
		% precede each author name, affiliation/snail-mail address and
		% e-mail address. Additionally, tag each line of
		% affiliation/address with \affaddr, and tag the
		% e-mail address with \email.
		%
		% 1st. author
		\alignauthor
		Sai Prashanth Chandramouli$^\dag$, Pierre-Marie Bajan$^\S$, Christopher Kruegel$^\ddag$, Giovanni Vigna$^\ddag$, Ziming Zhao$^\dag$, Adam Doup\'e$^\dag$, and Gail-Joon Ahn$^\dag$\\
		\affaddr{Arizona State University$^\dag$, IRT SystemX$^\S$, and University of California, Santa Barbara$^\ddag$}\\
		\{saipc, zzhao30, doupe, gahn\}@asu.edu$^\dag$,
        pierre-marie.bajan@irt-systemx.fr$^\S$, \\
        \{chris, vigna\}@cs.ucsb.edu$^\ddag$
        \vspace{-5ex}
        }
		% 2nd. author
		%% \alignauthor

		%% \affaddr{University of California, Santa Barbara}\\
		%% pm.bajan@free.fr
		%% \alignauthor
		%% \\
		%% \affaddr{University of California, Santa Barbara}\\
		%% giovanni.vigna@gmail.com
		%% \and
		%% \alignauthor
		%% \\
		%% \affaddr{Arizona State University}\\
		%% Ziming.Zhao@asu.edu
		%% \alignauthor
		%% Adam Doup\'{e}\\
		%% \affaddr{Arizona State University}\\
		%% doupe@asu.edu
		%% \alignauthor
		%% Gail-Joon Ahn\\
		%% \affaddr{Arizona State University}\\
		%% Gail-Joon.Ahn@asu.edu
		% 3rd. author
		%% \alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
		%% 	one who did all the really hard work.}\\
		%% \affaddr{The Th{\o}rv{\"a}ld Group}\\
		%% \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
		%% \affaddr{Hekla, Iceland}\\
		%% \email{larst@affiliation.org}
		%% \and  % use '\and' if you need 'another row' of author names
		%% % 4th. author
		%% \alignauthor Lawrence P. Leipuner\\
		%% \affaddr{Brookhaven Laboratories}\\
		%% \affaddr{Brookhaven National Lab}\\
		%% \affaddr{P.O. Box 5000}\\
		%% \email{lleipuner@researchlabs.org}
		%% % 5th. author
		%% \alignauthor Sean Fogarty\\
		%% \affaddr{NASA Ames Research Center}\\
		%% \affaddr{Moffett Field}\\
		%% \affaddr{California 94035}\\
		%% \email{fogartys@amesres.org}
		%% % 6th. author
		%% \alignauthor Charles Palmer\\
		%% \affaddr{Palmer Research Laboratories}\\
		%% \affaddr{8600 Datapoint Drive}\\
		%% \affaddr{San Antonio, Texas 78229}\\
		%% \email{cpalmer@prl.com}
	% There's nothing stopping you putting the seventh, eighth, etc.
	% author on the opening page (as the 'third row') but we ask,
	% for aesthetic reasons that you place these 'additional authors'
	% in the \additional authors block, viz.
	%% \additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
	%% 	email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
	%% 	(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
	%% \date{30 July 1999}
	% Just remember to make sure that the TOTAL number of authors
	% is the number that will appear on the first page PLUS the
	% number that will appear in the \additionalauthors section.
	\renewcommand{\email}{e-\nobreak{}mail\xspace}
	\maketitle

	\input{abstract}
